Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-21 paper.tex
Correcting @mgarenas name
Revised conclusion and introduction.
Addding a complete explanation of the book selling cycle and adding also more features to future work.

Closes #25
Closes #21

And I think that #11 should be closed too if @unintendedbear agrees.

\author[ugr]{Pedro A. Castillo}
\ead{pacv@ugr.es}
\author[ugr]{Antonio M. Mora}
\ead{amorag@geneura.ugr.es}
\author[abd]{H. Faris}
\ead{hossam.faris@ju.edu.jo}
\author[ugr]{J.J. Merelo}
\ead{jmerelo@geneura.ugr.es}
\author[ugr]{Pablo Garc\'{\i}a-S\'anchez}
\ead{pablogarcia@ugr.es}
\author[ugr]{Antonio J. Fern\'andez-Ares}
\ead{antares.es@gmail.com}
\author[ugr]{Paloma De las Cuevas}
\ead{palomacd@ugr.es}
\author[ugr]{María I. García-Arenas}
\ead{mgarenas@ugr.es}

@@

Therefore, in this work we analyse the data by means of different data mining methods and create predictive models that can be mainly used as decision-aid tools for book publishers. Then, they will be able to combine their expert knowledge about the market with the created forecasting models in order to get a reliable estimation of book sales.

% Antonio - I think this is the main idea we have to sell in this paper. Due to the  difficulty of the book sales market (and its variables), we cannot give an accurate tool for predicting book sales, but a decision-aid tool for publishers. Do you agree?
% (Paloma) Agree

@@

\subsection{Decision trees for best seller}
\label{subsec:decision_trees}

@@

This is a very challenging problem in this industry, because printing a higher 
number of volumes than those finally sold will lead to losses, while printing an adequate number of copies will optimise sales and company earnings.
In addition, there are several difficulties inherent to the new book sales forecasting, such as the limited amount of historical data to consider or the variability of the market (fashions, seasonality), which do a difficult task finding an adequate forecasting method.

A dataset consisting of 6000 books provided by the Spanish publishing company Trevenque Editorial S.L. has been used. These data have been analysed by means of Self-Organizing Maps as a visualisation tool, and two other Feature Selection techniques, namely a correlation-based feature subset evaluation method, and an adaptation of relief for attribute estimation. Using these methods the most relevant variables when predicting sales have been determined, while unrelated or superfluous ones have been removed.

Four different datasets have also been extracted from the original one, each one corresponding to a Publishing house which we have considered as representative: the one with the most number of sales, the one with the medium number of sales, with the most varied sales (different books), and with a medium number of different books sold.

@@

As a conclusion, M5P yields the best results overall, obtaining the best accuracy 
(lowest error) on average, even with acceptable values regarding the training time.
In addition, the Decision Trees obtained with this method have been presented 
as an excellent decision-aid tool for publishers, since they are accurate 
and quite easy to understand and apply. 
They are also able to provide insights on the decisions that have a higher influence on the 
expected sales 
%print-run 
for these publishers.

This, compared to the output of black-box models such as artificial neural networks, was a determining advantage from the point of view of the needs of experts and Trevenque company.

%Moreover, proposed method was validated by the company and incorporated in a 
%business intelligence tool for publishing companies. %FERGU: no hay más info de esto? estaría guay describirlo

@@

Overall, this study contributes to the literature by proposing the use of different soft-computing standard techniques to solve a new challenging problem.
Moreover, proposed method could be implemented, not only in the publishing 
industry, but also in other domains where the specificity of products is similar, and might be of interest to other academic researches and industrial practitioners.
% Antonio - I don't know if we should say this...

@@

As future work, it would be interesting to compare the obtained forecasting results with those yielded by other soft-computing methods, such as genetic programming or fuzzy logic.
Moreover, even if the methods have been configured to obtain the best forecasting results, it would be of interest carrying out some automatic parameter-tuning procedure by means of optimisation meta-algorithms, 
% Antonio - add an ESWA reference to this. :D
for instance.

>>>>

\author[ugr]{Pedro A. Castillo}
\ead{pacv@ugr.es}
\author[ugr]{Antonio M. Mora}
\ead{amorag@geneura.ugr.es}
\author[abd]{H. Faris}
\ead{hossam.faris@ju.edu.jo}
\author[ugr]{J.J. Merelo}
\ead{jmerelo@geneura.ugr.es}
\author[ugr]{Pablo Garc\'{\i}a-S\'anchez}
\ead{pablogarcia@ugr.es}
\author[ugr]{Antonio J. Fern\'andez-Ares}
\ead{antares.es@gmail.com}
\author[ugr]{Paloma De las Cuevas}
\ead{palomacd@ugr.es}
\author[ugr]{Mar\'ia I. Garc\'ia-Arenas}
\ead{mgarenas@ugr.es}

@@

In Spain, the process of releasing a book goes like this: the
publisher decides, based on past experience, how many books to
print. These books are distributed to points of sale, but also given
out to reviewers and literary magazines, the number of these will
depend on how many you have printed. Books then go, in some cases, to
the {\em novelty} table, that is, prominently displayed in the
bookstore, shown in the window, or highlighted using props or other
kind of advertisement. Books stay for sale for as long as the
publisher or the store want until the bookseller decides to return it
to the publisher or just, in some cases, move it away from shelves to
storage. Books returned to the publisher are pulped, sold back or
given to the author or distributed in second-hand channels such as
book stalls or second-hand bookstores. If the print run has been fully
distributed and there are more requests from bookstores, on the other
hand, a new print run is made and distributed to bookstores. 
Even if the process has changed
in the last few years since Amazon started to sell in Spain, which
actually happened {\em after} the data used for this paper was
collected, it roughly stays the same. Other countries will have a
similar model, although scale will be different.

Our intention in this paper is to find out the main factor influencing
sales in order to give a tool that the publisher can use to decide how
many books should be printed, as well as how to leverage these printed
copies to maximize sales using the decision variables under his
control. That is why, using data obtained from a  company that sells
software for publishers, we analyse it by means of different data
mining methods and create predictive models that can be mainly used as
decision-aid tools for book publishers. With these models, publishers
will be able to 
combine their expert knowledge about the market with the created
forecasting models in order to get a reliable estimation of book
sales, and, based on it, act upon it to maximize the books sold for a
particular print run.

@@

\subsection{Case study: publisher with the most sales}
\label{subsec:decision_trees}

@@

This is a very challenging problem in this industry, because printing
a much higher 
number of volumes than those finally sold will lead to losses, while
printing an adequate number of copies will optimise sales and company
earnings.  
In addition, there are several difficulties inherent to the new book
sales forecasting, such as the limited amount of historical data to
consider or the variability of the market (fashions, seasonality),
which do a difficult task finding an adequate forecasting method.

A dataset consisting of 6000 books provided by the Spanish publishing
company Trevenque Editorial S.L. has been used. This data has been
analysed by means of Self-Organizing Maps as a visualisation tool, and
two other Feature Selection techniques, namely a correlation-based
feature subset evaluation method, and an adaptation of relief for
attribute estimation. Using these methods the most relevant variables
when predicting sales have been determined, while unrelated or
superfluous ones have been removed.

Four different datasets have also been extracted from the original
one, each one corresponding to a publishing house which we have
considered as representative: the one with the most number of sales,
the one with the medium number of sales, with the most varied sales
(different books), and with a medium number of different books sold.

@@

As a conclusion, M5P yields the best results overall, obtaining the best accuracy 
(lowest error) on average, even with acceptable values regarding the training time.
In addition, the Decision Trees obtained with this method have been
shown to be an excellent decision-aid tool for publishers, since they are accurate 
and quite easy to understand and apply. 
They are also able to provide insights on the decision variables that
have a higher influence on the predicted sales for these publishers.

This, compared to the output of black-box models such as artificial
neural networks, was a determining advantage from the point of view of
the needs of experts and the company that initially contacted us for
this work.

@@

Overall, this study contributes to the literature by proposing the use
of different soft-computing standard techniques to solve a new
challenging problem. 
Moreover, proposed method, consisting in selecting features and
applying different models for different types of publishers could be
implemented, not only in the publishing  
industry, but also in other domains where the specificity of products
is similar such as novelty items or toys, and might be of interest to other academic researches and
industrial practitioners.  
% Antonio - I don't know if we should say this...

@@

As future work, it would be interesting to compare the obtained
forecasting results with those yielded by other soft-computing
methods, such as genetic programming or fuzzy logic. 
Moreover, even if the methods have been configured to obtain the best
forecasting results, it would be of interest carrying out some
automatic parameter-tuning procedure by means of optimisation
meta-algorithms,  
% Antonio - add an ESWA reference to this. :D
for instance. If data for other countries were available, it would be
interesting to observe, and factor in the method, country differences,
even considering the same book and how it sells in different
countries.
